---
title: "Event Study: Brent Spence Bridge Corridor Impact"
author: "Gemini CLI"
format: html
---

```{r setup, include=FALSE}
library(tidyverse)
library(scales)

events <- read_csv("data/bsb_event_analysis.csv", show_col_types = FALSE)
growth <- read_csv("data/bsb_long_term_growth.csv", show_col_types = FALSE)
distances <- read_csv("data/zip_bsb_distances.csv", show_col_types = FALSE)
```

## Executive Summary

This analysis tracks home price evolution near the **Brent Spence Bridge (BSB)** corridor in response to major project milestones. We find a significant "landing zone" effect: ZIP codes within 1 mile of the project (e.g., 45203, 41014) have outperformed the broader region by **8.5 percentage points** since the 2020 fire.

## Long-Term Appreciation (2020 - 2026)

The table below shows the average price growth from Jan 2020 to April 2026, categorized by distance from the I-75/BSB corridor.

```{r growth-table, echo=FALSE}
growth %>%
  rename(Distance_Zone = dist_meters, Pct_Growth = Price_Growth_Since_2020) %>%
  knitr::kable(digits = 2, caption = "Average Price Growth Since Jan 2020")
```

## Event Analysis

We analyzed four major "shocks" to the project timeline. For each event, we normalized prices to the month of the announcement (Index = 100).

### 1. The $1.6B Federal Grant (Dec 2022)

This was the single largest funding commitment in the project's history.

```{r grant-plot, echo=FALSE}
events %>%
  filter(Event == "$1.6B Federal Grant") %>%
  ggplot(aes(x = Date, y = Price_Index, color = Zone)) +
  geom_line(size = 1) +
  geom_vline(xintercept = as.numeric(as.Date("2022-12-29")), linetype = "dashed", color = "red") +
  labs(title = "Home Price Response to $1.6B Grant",
       subtitle = "Red dashed line indicates announcement date",
       y = "Price Index (Event Month = 100)",
       x = "Date") +
  theme_minimal()
```

### 2. Contractor Award (July 2023)

The award to Walsh Kokosing signaled that the project was moving from "political talk" to "physical execution."

```{r award-plot, echo=FALSE}
events %>%
  filter(Event == "Contractor Award") %>%
  ggplot(aes(x = Date, y = Price_Index, color = Zone)) +
  geom_line(size = 1) +
  geom_vline(xintercept = as.numeric(as.Date("2023-07-27")), linetype = "dashed", color = "red") +
  labs(title = "Home Price Response to Contractor Award",
       y = "Price Index (Event Month = 100)",
       x = "Date") +
  theme_minimal()
```

## Neighborhood Focus: The "Landing Zone"

The most impacted ZIP codes are **45203** (Queensgate/West End) and **41014** (West Covington). These areas are directly adjacent to the new bridge landings and have seen the most intense speculative activity.

```{r landing-zone, echo=FALSE}
distances %>%
  filter(dist_meters < 1000) %>%
  arrange(dist_meters) %>%
  knitr::kable(caption = "ZIP Codes within 1km of BSB Corridor")
```
